---
title: "Homework-7"
author: "Juliana Dau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

data("iris")


```

# 1. Examine the structure of the iris data set. How many observations and variables are in the data set?
```
There are 150 observations and 5 variables (Sepal.Lenght, Sepal Width, Petal.Length,Petal.Width and species)
```
```{r}
library(tidyverse)
data("iris")
print(iris)
```


# 2. Create a new data frame iris1 that contains only the species virginica and versicolor with sepal lengths longer than 6 cm and sepal widths longer than 2.5 cm. How many observations and variables are in the data set? 
```
56 observations with 5 variables
```
```{r}

library(tidyverse)
data("iris")
class(iris)
iris1<-filter(iris, Species != "setosa", Sepal.Length > 6, Sepal.Width > 2.5)
print(iris1)

```

#3. Now, create a iris2 data frame from iris1 that contains only the columns for Species, Sepal.Length, and Sepal.Width. How many observations and variables are in the data set?
```
56 observations with 3 variables
```
```{r}
iris2<-select(iris1, Sepal.Length, Sepal.Width, Species)
print(iris2)
```

#4. Create an iris3 data frame from iris2 that orders the observations from largest to smallest sepal length. Show the first 6 rows of this data set.

```{r}
iris3<-arrange(iris2, by = desc(Sepal.Length))
head(iris3)
```
#5. Create an iris4 data frame from iris3 that creates a column with a sepal area (length * width) value for each observation. How many observations and variables are in the data set?
