---
title: "Homework-8"
author: "Juliana Dau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Using sample Code

```{r}
library(ggplot2) 
library(MASS) 
```

```{r}
z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
```
#Histogram. 
#Observation: R studio indicated that some were deprecated and sugested to change size to linewith so I did it. 
```{r}
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p1)
```

#Empirical density curve 
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",linewidth=0.75)
print(p1)
```

#Maximum likelihood parameters for normal
```{r}
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"]
```

#Plot normal probability density
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

#Plot exponential probability density
```{r}
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2

```
#Plot uniform probability density
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3

```
#Plot gamma probability density
```{r}
gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```
#Plot beta probability density
```{r}
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

```

Visually gamma or beta probability density seemed to be the better fit. 

# 2. Using Own data/External data
#Similar to Homework 6 used the quantification of surfactant protein C (SPC) found in the bronchoalveolar lavage fluid across 16 animals.

```{r}
Z <- read.table("SPC.quantification.homework8.csv",header=TRUE,sep=",")
str(Z)
summary(Z)

```
#Histogram. 

```{r}
p2 <- ggplot(data=Z, aes(x=SPC, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p2)

```

#Empirical density curve 
```{r}
p2 <-  p2 +  geom_density(linetype="dotted",size=0.75)
print(p2)

```

#Maximum likelihood parameters for normal
```{r}
normPars2 <- fitdistr(Z$SPC,"normal")
print(normPars2)
str(normPars2)
normPars2$estimate["mean"] 
```

#Plot normal probability density
```{r}
meanML <- normPars2$estimate["mean"]
sdML <- normPars2$estimate["sd"]

xval <- seq(0,max(Z$SPC),len=length(Z$SPC))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(Z$SPC), args = list(mean = meanML, sd = sdML))
 p2 + stat
```

#Plot exponential probability density
```{r}
expoPars <- fitdistr(Z$SPC,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(Z$SPC), args = list(rate=rateML))
 p2 + stat + stat2

```
#Plot uniform probability density
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(Z$SPC), args = list(min=min(Z$SPC), max=max(Z$SPC)))
 p2 + stat + stat2 + stat3
```
#Plot gamma probability density
#observation:due to error from fitting, defined the value of lower so it could run. For 0.001 was still giving error.
```{r}
gammaPars <- fitdistr(Z$SPC,dgamma,list(shape=1,rate=0.1),lower=0.01)
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(Z$SPC), args = list(shape=shapeML, rate=rateML))
 p2 + stat + stat2 + stat3 + stat4
```
#Plot beta probability density
```{r}
pSpecial <- ggplot(data=Z, aes(x=SPC/(max(SPC + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=Z$SPC/max(Z$SPC + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(Z$SPC), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

```

Although no fit was perfect, uniform distribution showed the best model for the data. 