---
title: "Homework-5"
author: "Juliana Dau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 1.

# Will give the single random interger between 1 and 10.
```{r}
n_dims <- sample(3:10,1)
print(n_dims)
```

# Based on that, write a general function to get a vector of consecutive integers from 1 to n_dims2.

```{r}
my_vec <- seq(from=1, to=n_dims^2)
print(my_vec)

```
```
# Since it was random when n_dims result was 3 the my_vec result was:
[1] 1 2 3 4 5 6 7 8 9
#When n_dims result was 9 the my_vec result was:
[1]  1  2  3  4  5  6  7  8  9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36 37 38 39 40 41 42 43
[44] 44 45 46 47 48 49 50 51 52 53 54 55 56 57 58 59 60 61 62 63 64 65 66 67 68 69 70 71 72 73 74 75 76 77 78 79 80 81

```
# Use the sample function to randomly reshuffle these values.
```{r}

shuffled_vector <- sample(my_vec) 
print(shuffled_vector) 
```

# Create a square matrix with these elements.Print out the matrix.
```{r}
m <- matrix(data=my_vec,nrow=n_dims)
print(m)
```

Find a function in r to transpose the matrix.print it out again and note how it has changed.

```{r}
my_matrix=matrix(data=my_vec,nrow=n_dims)
transposed_matrix <- t(my_matrix)
print(transposed_matrix)
```


# Calculate the sum and the mean of the elements in the first row and then the last row. Assuming that the desired result is of the transposed matrix:
```{r}
first_row_sum <- sum(transposed_matrix[1,])
print(first_row_sum)

first_row_mean <- mean(transposed_matrix[1,]) 
print(first_row_mean)
```
```{r}
last_row_sum <- sum(transposed_matrix[n_dims,])
print (last_row_sum)
```
```{r}
last_row_mean <- mean(transposed_matrix[n_dims,])
print(last_row_mean)

```

# Read about the eigen() function and use it on your matrix.
# Look carefully at the elements of $values and $vectors in the output. What kind of numbers are these?
```{r}
ev <- eigen(transposed_matrix)
(values <- ev$values)
(vectors <- ev$vectors)
```

# Dig in with the typeof() function to figure out their type.
```{r}
typeof(vectors)

typeof(values)
```

# Checked and was able to re-run it and create a matrix of different size because n_dims will change.

# Problem 2.
#Create a list with the following named elements:
#my_matrix, which is a 4 x 4 matrix filled with random uniform values

```{r}
my_matrix=matrix(runif(16),nrow=4,ncol=4)
print(my_matrix)
```
#my_logical which is a 100-element vector of TRUE or FALSE values. Do this efficiently by setting up a vector of random values and then applying an inequality to it.
```{r}
my_logical <- sample(c(TRUE, FALSE), size = 100, replace = TRUE, prob = c(0.5, 0.5)) 
print(my_logical)
```
#my_letters, which is a 26-element vector of all the lower-case letters in random order.
```{r}
my_letters <- sample(letters, 26) 
print(my_letters)
```
#create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.
```{r}
my_list <- list(my_matrix,
                my_logical,
                my_letters)
my_list <- list(my_matrix[[2,2]], my_logical[2], my_letters[2])
print(my_list)

```
#use the typeof() function to confirm the underlying data types of each component in this list
```{r}
type_my_matrix <- typeof(my_matrix[[2,2]])
print(type_my_matrix)
type_my_logical <- typeof(my_logical[2])
print(type_my_logical)
type_my_letters <- typeof(my_letters[2])
print(type_my_letters)

```
#combine the underlying elements from the new list into a single atomic vector with the c() function.

```{r}
vector2 <- c(my_matrix[[2,2]],my_logical[2],my_letters[2])
print(vector2)

```
#what is the data type of this vector?
```{r}
typeof(vector2)
```

# Problem 3.
# Create a data frame with the two variables (= columns) and 26 cases (= rows) below:

#Call the first variable my_unis and fill it with 26 random uniform values from 0 to 10
#Call the second variable my_letters and fill it with 26 capital letters in random order
```{r}
my_units <- runif(n=26, min=0, max=10)
my_letters <- sample(LETTERS, size = 26)
d_frame <- data.frame(my_units,my_letters)
print(d_frame)
str(d_frame)

```
#For the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.
```{r}

d_frame[sample(x=1:26,4),1] <- NA
print(d_frame)

```

#For the first variable, write a single line of R code to identify which rows have the missing values.

```{R}
which(is.na(d_frame), arr.ind=TRUE)

```

#Re-order the entire data frame to arrange the second variable in alphabetical order

```{R}
my_units <- runif(n=26, min=0, max=10)
my_letters <- rep(c(LETTERS))
d_frame <- data.frame(my_units,my_letters)
print(d_frame)

```

#Calculate the column mean for the first variable.

```{R}

mean(d_frame[, 1])

```